---
title: "Supplement"
author: "Rebecca Martin"
date: "2/1/2018"
output: 
    html_document:
        df_print: 'paged'
        toc: true
        toc_float:
            collapsed: false
            smooth_scroll: true
        number_sections: true
        code_download: true
        self_contained: true
        code_folding: 'hide'
---
    
---
# Set up 
## Settings

```{r setDirs}
root <- rprojroot::find_rstudio_root_file()
dataDir <- file.path(root, 'data')
codeDir <- file.path(root, 'code')
figureDir <- file.path(root, 'figures')
```

## Packages

```{r libraries, message=FALSE, warning=FALSE}
library(reshape2)
library(plyr)
library(tidyverse)
library(lme4)
library(lmerTest)
library(car)
source(file.path(codeDir, "CreateFunctions.R"))
source(file.path(codeDir, "correlate_multiple_specific_variables.R"))
```

## Read in data and make subsets

```{r readdata}
phase2merged <- read.table(file.path(dataDir, 'new_anon.txt'), header=TRUE, sep='\t')
teens <- read.table(file.path(dataDir, 'teensonly.txt'), header=TRUE, sep='\t')
adults <- read.table(file.path(dataDir, 'adultsonly.txt'), header=TRUE, sep='\t')

phase2merged$group = factor(phase2merged$group, labels = c("Adults", "Adolesc")) # changes levels for graphing
```

## Make subsets

```{r liked-disliked}
likedAll <- phase2merged %>% 
    filter(phase1rating > 4)

likedTeens <- teens %>% 
    filter(phase1rating > 4)

likedAdults <- adults %>% 
    filter(phase1rating > 4)

dislikedAll <- phase2merged %>% 
    filter(phase1rating < 4)

dislikedTeens <- teens %>% 
    filter(phase1rating < 4)

dislikedAdults <- adults %>% 
    filter(phase1rating < 4)

neutAll <- phase2merged %>% 
    filter(phase1rating == 4)

neutTeens <- teens %>% 
    filter(phase1rating == 4)

neutAdults <- adults %>% 
    filter(phase1rating == 4)
```

## Make matched dataset based on items both teens and adults gave similar ratings to (i.e. ratings that were within .5 points of each other)

```{r groupmatched}
matchedAll <- phase2merged %>%  dplyr::filter(condimage %in% c(102, 105, 120, 123, 125, 126, 136, 137, 138, 139,141, 142, 144, 147, 148, 149, 150, 151, 153, 158, 159, 160, 162, 164, 165, 167, 168, 170, 172,173, 175, 176, 177, 178, 179, 181, 182, 184, 187, 188, 189, 208, 227, 228, 229, 231, 232,	233, 234, 235, 236, 237, 239, 241, 242, 243, 250, 257, 259, 266, 268, 277, 281, 282, 285, 288, 289))

matchedLikeAll <- matchedAll %>% filter(phase1rating > 4)
matchedLikeTeens <- matchedLikeAll %>% filter(group == "Adolesc")
matchedLikeAdults <- matchedLikeAll %>% filter(group == "Adults")
```

## Grand mean center and get adjusted means for teens and adults for plotting (liked only)

```{r meanCenter}
# all
p1_gmcenter = scale(likedAll$phase1rating, scale=F)
likedAll$p1rating_gmcenter <- p1_gmcenter
likedAll$p1rating_gmcenter <- as.numeric(likedAll$p1rating_gmcenter)

# residuals
adjmeans_all = lmer(phasediffrating ~ p1rating_gmcenter+(1+p1rating_gmcenter|subjid), data=likedAll)
likedAll$resid <- resid(adjmeans_all)

## Center by age group
likedAll <- within(likedAll, {phase1ratingGM = ave(phase1rating, group , FUN = mean)})
likedAll$phase1ratingGC <- likedAll$phase1rating - likedAll$phase1ratingGM

## Make adjusted change scores (residuals controlling for time 1 ratings) for graphing
adjmeans_phasediffrating <- lmer(phasediffrating ~ phase1ratingGC + (1 + phase1ratingGC|subjid), data=likedAll)
likedAll$adjphasediffratingGV <- resid(adjmeans_phasediffrating)
```

## Grand mean center and get adjusted means for teens and adults for plotting (MATCHED liked only)

```{r meanCenterMatched}
# all
p1_gmcenter = scale(matchedLikeAll$phase1rating, scale=F)
matchedLikeAll$p1rating_gmcenter <- p1_gmcenter
matchedLikeAll$p1rating_gmcenter <- as.numeric(matchedLikeAll$p1rating_gmcenter)

# residuals
adjmeans_all = lmer(phasediffrating ~ p1rating_gmcenter+(1+p1rating_gmcenter|subjid), data=matchedLikeAll)
matchedLikeAll$resid <- resid(adjmeans_all)

## Center by age group
matchedLikeAll <- within(matchedLikeAll, {phase1ratingGM = ave(phase1rating, group , FUN = mean)})
matchedLikeAll$phase1ratingGC <- matchedLikeAll$phase1rating - matchedLikeAll$phase1ratingGM

## Make adjusted change scores (residuals controlling for time 1 ratings) for graphing
adjmeans_phasediffrating <- lmer(phasediffrating ~ phase1ratingGC + (1 + phase1ratingGC|subjid), data=matchedLikeAll)
matchedLikeAll$adjphasediffratingGV <- resid(adjmeans_phasediffrating)
```

## Make theme 

```{r make_theme, echo=FALSE, results='hide', message=FALSE}
beckys.theme = theme(panel.background = element_rect(fill='transparent'),
                        axis.line = element_line(color='black'),
                        panel.grid.minor = element_line(color='transparent'),
                        axis.title.x = element_text(size=20, vjust=-.25),
                        axis.title.y = element_text(size=20, vjust=1),
                        axis.text.x = element_text(size=16, colour="black"),
                        axis.text.y = element_text(size=16, colour="black"),
                        legend.text=element_text(size=14))

beckys.theme.conference = theme(panel.background = element_rect(fill='transparent'),
                        axis.line = element_line(color='black'),
                        panel.grid.minor = element_line(color='transparent'),
                        axis.title.x = element_text(size=24, vjust=-.25, face = "bold"),
                        axis.title.y = element_text(size=24, vjust=1, face = "bold"),
                        axis.text.x = element_text(size=16, colour="black"),
                        axis.text.y = element_text(size=16, colour="black"),
                        legend.text=element_text(size=16),
                        strip.text.y = element_text(size = 16),
                        strip.text.x = element_text(size = 16))
```

# Plot 

## Distribution of ratings density plot LIKED

```{r distPlot}
distbytrial = ggplot(likedAll, aes(x=phase1rating,fill=group)) + 
  geom_density(adjust=2, alpha=.7) + # add , colour=NA if want to take out black outlines
  beckys.theme +
  scale_x_continuous(limits = c(1, 7), breaks=seq(1, 7,1)) +
  scale_fill_manual(values=c("#1f78b4","#a6cee3")) + 
  scale_linetype_manual(values=c("#1f78b4","#a6cee3")) + 
  guides(fill = guide_legend(reverse = TRUE, override.aes = list(colour = NULL))) +
  xlab("Initial Ratings") +
  ylab("Density") +
  #theme(legend.key = element_rect(colour = "black"))
  beckys.theme.conference +
  theme(axis.line.x=element_line(color = 'black'),legend.position = "none", axis.line.y=element_line(color = 'black'))

distbytrial
```

## Distribution of ratings density plot MATCHED LIKED

```{r distPlotMatched}
distbytrial = ggplot(matchedLikeAll, aes(x=phase1rating,fill=group)) + 
  geom_density(adjust=2, alpha=.7) + # add , colour=NA if want to take out black outlines
  beckys.theme +
  scale_x_continuous(limits = c(1, 7), breaks=seq(1, 7,1)) +
  scale_fill_manual(values=c("#1f78b4","#a6cee3")) + 
  scale_linetype_manual(values=c("#1f78b4","#a6cee3")) + 
  guides(fill = guide_legend(reverse = TRUE, override.aes = list(colour = NULL))) +
  xlab("Initial Ratings") +
  ylab("Density") +
  #theme(legend.key = element_rect(colour = "black"))
  beckys.theme.conference +
  theme(axis.line.x=element_line(color = 'black'),legend.position = "none", axis.line.y=element_line(color = 'black'))

distbytrial
```

## Average ratings by group LIKED

```{r avgPlot}
overallaverages <- plyr::ddply(likedAll, c("subjid","group"), summarise, phase1rating=mean(phase1rating))
overallaverages$group = factor(overallaverages$group, levels = rev(levels(factor(overallaverages$group))))
overallavg_summary = summarySE(overallaverages, measurevar="phase1rating", groupvars=c("group"))

overallavg_summary

overallavg_point <-  ggplot(overallaverages, aes(x=group, y=phase1rating, color=group, group=group)) 

overallavg_point + geom_point(position=position_jitterdodge(dodge.width=.7, jitter.width = .2), size=3, alpha=.7) +
  #scale_color_brewer(palette="Paired") +
scale_color_manual(values=c("#6baed6","#1f78b4")) + 
  geom_errorbar(data=overallavg_summary, aes(ymin=phase1rating-se, ymax=phase1rating+se), width=.3, position=position_dodge(.7), size=1.5, alpha=1, color="black") +
  geom_point(data=overallavg_summary, position=position_dodge(.7), stat="identity", size=5, mapping=aes(x=group, y=phase1rating, color=group), alpha=1, color="black") + 
  xlab("Age Group") + 
  ylab("Average Initial Rating") + 
  scale_y_continuous(limits = c(1, 7), breaks=seq(1, 7, 1)) +
  beckys.theme.conference +
  #geom_hline(aes(yintercept=0), size=.75) + 
  theme(axis.line.x=element_line(color = 'black'),legend.position = "none", axis.line.y=element_line(color = 'black'))

# ggsave("figures/meanRatingbyGroup.pdf", width=5, height=7, dpi=300)
```

## Average ratings by group MATCHED LIKED

```{r avgPlotMatched}
overallaverages <- plyr::ddply(matchedLikeAll, c("subjid","group"), summarise, phase1rating=mean(phase1rating))
overallaverages$group = factor(overallaverages$group, levels = rev(levels(factor(overallaverages$group))))
overallavg_summary = summarySE(overallaverages, measurevar="phase1rating", groupvars=c("group"))

overallavg_summary

overallavg_point <-  ggplot(overallaverages, aes(x=group, y=phase1rating, color=group, group=group)) 

overallavg_point + geom_point(position=position_jitterdodge(dodge.width=.7, jitter.width = .2), size=3, alpha=.7) +
  #scale_color_brewer(palette="Paired") +
scale_color_manual(values=c("#6baed6","#1f78b4")) + 
  geom_errorbar(data=overallavg_summary, aes(ymin=phase1rating-se, ymax=phase1rating+se), width=.3, position=position_dodge(.7), size=1.5, alpha=1, color="black") +
  geom_point(data=overallavg_summary, position=position_dodge(.7), stat="identity", size=5, mapping=aes(x=group, y=phase1rating, color=group), alpha=1, color="black") + 
  xlab("Age Group") + 
  ylab("Average Initial Rating") + 
  scale_y_continuous(limits = c(1, 7), breaks=seq(1, 7, 1)) +
  beckys.theme.conference +
  #geom_hline(aes(yintercept=0), size=.75) + 
  theme(axis.line.x=element_line(color = 'black'),legend.position = "none", axis.line.y=element_line(color = 'black'))

# ggsave("figures/meanRatingbyGroup.pdf", width=5, height=7, dpi=300)
```

## Summary stats for mean change group centered LIKED

```{r groupCentSummary}
# Summarise phasediffrating and adj phasediffrating by subject
## categorically
averagesbygroup <- plyr::ddply(likedAll, c("subjid", "Phase1PCond2", "group"), summarise, adjratingchange=mean(adjphasediffratingGV))

averagesbygroup$group = factor(averagesbygroup$group, levels = rev(levels(factor(averagesbygroup$group))))

## Change variables of interest to factors for graphing
averagesbygroup$Phase1PCond2 = factor(averagesbygroup$Phase1PCond2, labels = c("Less", "Agree", "More", "NoFb")) # changes levels for graphing

groupmc_summary <-  summarySEwithin(averagesbygroup, measurevar="adjratingchange", withinvars=c("Phase1PCond2","group"), idvar="subjid")

groupmc_summary
```

## Group centered adjusted mean change LIKED

```{r plotMeanChangeLiked}
age_point <-  ggplot(averagesbygroup, aes(x=Phase1PCond2, y=adjratingchange, color=group, group=group)) 

age_point + geom_point(position=position_jitterdodge(dodge.width=.7, jitter.width = .2), size=2, alpha=.5) +
    #scale_color_brewer(palette="Paired") +
    scale_color_manual(values=c("#6baed6","#1f78b4")) + 
  geom_errorbar(data=groupmc_summary, aes(ymin=adjratingchange-se, ymax=adjratingchange+se), width=.4, position=position_dodge(.7), size=1, alpha=1, color="black") +
  geom_point(data=groupmc_summary, position=position_dodge(.7), stat="identity", size=4, mapping=aes(x=Phase1PCond2, y=adjratingchange), alpha=1, color="black") + 
  xlab("Peer Feedback") + 
  ylab("Change in Preference") + 
  #scale_y_continuous(limits = c(-.7, .7), breaks=seq(-.7, .7,.1), labels=function(x) round(x, 2)) +
  xlim("NoFb", "Agree", "More", "Less") +
  beckys.theme.conference +
  geom_hline(aes(yintercept=0), size=.75) + 
  theme(axis.line.x=element_line(color = 'black'),legend.position = "none", axis.line.y=element_line(color = 'black'))

#ggsave("figures/BehavMainEffectsDiss.pdf", width=7, height=5, dpi=300)
```

## Summary stats for mean change group centered MATCHED LIKED

```{r groupCentSummaryMatched}
# Summarise phasediffrating and adj phasediffrating by subject
## categorically
averagesbygroup <- plyr::ddply(matchedLikeAll, c("subjid", "Phase1PCond2", "group"), summarise, adjratingchange=mean(adjphasediffratingGV))

averagesbygroup$group = factor(averagesbygroup$group, levels = rev(levels(factor(averagesbygroup$group))))

## Change variables of interest to factors for graphing
averagesbygroup$Phase1PCond2 = factor(averagesbygroup$Phase1PCond2, labels = c("Less", "Agree", "More", "NoFb")) # changes levels for graphing

groupmc_summary <-  summarySEwithin(averagesbygroup, measurevar="adjratingchange", withinvars=c("Phase1PCond2","group"), idvar="subjid")

groupmc_summary
```

### Group centered adjusted mean change MATCHED LIKED

```{r plotMeanChangeMatched}
age_point <-  ggplot(averagesbygroup, aes(x=Phase1PCond2, y=adjratingchange, color=group, group=group)) 

age_point + geom_point(position=position_jitterdodge(dodge.width=.7, jitter.width = .2), size=2, alpha=.5) +
    #scale_color_brewer(palette="Paired") +
    scale_color_manual(values=c("#6baed6","#1f78b4")) + 
  geom_errorbar(data=groupmc_summary, aes(ymin=adjratingchange-se, ymax=adjratingchange+se), width=.4, position=position_dodge(.7), size=1, alpha=1, color="black") +
  geom_point(data=groupmc_summary, position=position_dodge(.7), stat="identity", size=4, mapping=aes(x=Phase1PCond2, y=adjratingchange), alpha=1, color="black") + 
  xlab("Peer Feedback") + 
  ylab("Change in Wanting") + 
  #scale_y_continuous(limits = c(-.7, .7), breaks=seq(-.7, .7,.1), labels=function(x) round(x, 2)) +
  xlim("NoFb", "Agree", "More", "Less") +
  beckys.theme.conference +
  geom_hline(aes(yintercept=0), size=.75) + 
  theme(axis.line.x=element_line(color = 'black'),legend.position = "none", axis.line.y=element_line(color = 'black'))

#ggsave("figures/BehavMainEffectsDiss.pdf", width=7, height=5, dpi=300)
```

# Statistics

```{r stats}
# Does age group predict baseline ratings? 
# Liked Only
baseline = lmer(p1rating_gmcenter ~ group + (1|subjid), data=likedAll) 
summary(baseline) 
## Nope - no difference at baseline

# Matched Liked
baseline = lmer(p1rating_gmcenter ~ group + (1|subjid), data=matchedLikeAll) 
summary(baseline) 
# teens might like things slightly more on average with this matched ratings set 


## Is there an interaction with group? 
# Liked
groupinteraction = lmer(phasediffrating ~ p1rating_gmcenter+pos_neg*group+(1+p1rating_gmcenter+pos_neg|subjid), data=likedAll)
summary(groupinteraction)

# Matched Liked
groupinteraction = lmer(phasediffrating ~ p1rating_gmcenter+pos_neg*group+(1+p1rating_gmcenter+pos_neg|subjid), data=matchedLikeAll)
summary(groupinteraction)

###  treat pos/neg as factor

likedAll$pos_negFact <- as.factor(likedAll$pos_neg)
matchedLikeAll$pos_negFact <- as.factor(matchedLikeAll$pos_neg)

# Liked
groupinteraction = lmer(phasediffrating ~ p1rating_gmcenter+relevel(pos_negFact, "0")*group+(1+p1rating_gmcenter+pos_neg|subjid), data=likedAll)
summary(groupinteraction)

# Matched Liked
groupinteraction = lmer(phasediffrating ~ p1rating_gmcenter+relevel(pos_negFact, "0")*group+(1+p1rating_gmcenter+pos_neg|subjid), data=matchedLikeAll)
summary(groupinteraction)
```

