---
title: "BehavPaperCode"
author: "Rebecca Martin"
date: "7/11/2017"
output: 
    html_document:
        df_print: 'paged'
        toc: true
        toc_float:
            collapsed: false
            smooth_scroll: true
        number_sections: true
        code_download: true
        self_contained: true
        code_folding: 'hide'
---
# Set up 
## Settings

```{r setDirs}
root <- rprojroot::find_rstudio_root_file()
dataDir <- file.path(root, 'data')
codeDir <- file.path(root, 'code')
```

## Packages

```{r libraries, message=FALSE}
library(reshape2)
library(plyr)
library(tidyverse)
library(lme4)
library(lmerTest)
source(file.path(codeDir, "CreateFunctions.R"))
```

## Read in data

```{r readData, message=FALSE, warning=FALSE, include=FALSE}
raw <- readr::read_tsv(file.path(dataDir, 'raw.txt'))
phase2merged <- readr::read_tsv(file.path(dataDir, 'new_anon.txt'))
teens <- readr::read_tsv(file.path(dataDir, 'teensonly.txt'))
adults <- readr::read_tsv(file.path(dataDir, 'adultsonly.txt'))
averagedData <- readr::read_tsv(file.path(dataDir, 'all_avgd_subset.txt'))

phase2merged$group <- factor(phase2merged$group, labels = c("Adults", "Adolesc")) # changes levels for graphing
```


## Grand mean center and get adjusted means for plotting

```{r centerAndResidualize}
# all
p1_gmcenter = scale(phase2merged$phase1rating, scale=F)
phase2merged$p1rating_gmcenter <- p1_gmcenter
phase2merged$p1rating_gmcenter <- as.numeric(phase2merged$p1rating_gmcenter)

# residuals
adjmeans_all = lmer(phasediffrating ~ p1rating_gmcenter+(1+p1rating_gmcenter|subjid), data=phase2merged)
phase2merged$resid <- resid(adjmeans_all)

## Center by age group
phase2merged <- within(phase2merged, {phase1ratingGM = ave(phase1rating, group , FUN = mean)})
phase2merged$phase1ratingGC <- phase2merged$phase1rating - phase2merged$phase1ratingGM

## Make adjusted change scores (residuals controlling for time 1 ratings) for graphing
adjmeans_phasediffrating <- lmer(phasediffrating ~ phase1ratingGC + (1 + phase1ratingGC|subjid), data=phase2merged)
phase2merged$adjphasediffratingGV <- resid(adjmeans_phasediffrating)

```

## Make theme for plots

```{r makeTheme, include=FALSE}
beckys.theme = theme(panel.background = element_rect(fill='transparent'),
                        axis.line = element_line(color='black'),
                        panel.grid.minor = element_line(color='transparent'),
                        axis.title.x = element_text(size=20, vjust=-.25),
                        axis.title.y = element_text(size=20, vjust=1),
                        axis.text.x = element_text(size=16, colour="black"),
                        axis.text.y = element_text(size=16, colour="black"),
                        legend.text=element_text(size=14))

beckys.theme.conference = theme(panel.background = element_rect(fill='transparent'),
                        axis.line = element_line(color='black'),
                        panel.grid.minor = element_line(color='transparent'),
                        axis.title.x = element_text(size=24, vjust=-.25, face = "bold"),
                        axis.title.y = element_text(size=24, vjust=1, face = "bold"),
                        axis.text.x = element_text(size=16, colour="black"),
                        axis.text.y = element_text(size=16, colour="black"),
                        legend.text=element_text(size=16),
                        strip.text.y = element_text(size = 16),
                        strip.text.x = element_text(size = 16))
```

# Baseline differences between young adolescents and adults
## Distribution of ratings density plot

```{r distributionPlot, echo=FALSE}
distbytrial = ggplot(phase2merged, aes(x=phase1rating,fill=group)) + 
  geom_density(adjust=2, alpha=.7) + # add , colour=NA if want to take out black outlines
  beckys.theme +
  scale_x_continuous(limits = c(1, 7), breaks=seq(1, 7,1)) +
  scale_fill_manual(values=c("#1f78b4","#a6cee3")) + 
  scale_linetype_manual(values=c("#1f78b4","#a6cee3")) + 
  guides(fill = guide_legend(reverse = TRUE, override.aes = list(colour = NULL))) +
  xlab("Initial Ratings") +
  ylab("Density") +
  #theme(legend.key = element_rect(colour = "black"))
  beckys.theme.conference +
  theme(axis.line.x=element_line(color = 'black'),legend.position = "none", axis.line.y=element_line(color = 'black'))

distbytrial
```

## Calculate average ratings by group

```{r calculateAverageInitialRatings, include=FALSE}
overallaverages <- plyr::ddply(phase2merged, c("subjid","group"), summarise, phase1rating=mean(phase1rating))
overallaverages$group = factor(overallaverages$group, levels = rev(levels(factor(overallaverages$group))))
overallavg_summary = summarySE(overallaverages, measurevar="phase1rating", groupvars=c("group"))
overallavg_point <-  ggplot(overallaverages, aes(x=group, y=phase1rating, color=group, group=group)) 
```

## Plot average initial ratings

```{r plotAverageInitialRating, echo=FALSE}
overallavg_point + geom_point(position=position_jitterdodge(dodge.width=.7, jitter.width = .2), size=3, alpha=.7) +
scale_color_manual(values=c("#6baed6","#1f78b4")) + 
  geom_errorbar(data=overallavg_summary, aes(ymin=phase1rating-se, ymax=phase1rating+se), width=.3, position=position_dodge(.7), size=1.5, alpha=1, color="black") +
  geom_point(data=overallavg_summary, position=position_dodge(.7), stat="identity", size=5, mapping=aes(x=group, y=phase1rating, color=group), alpha=1, color="black") + 
  xlab("Age Group") + 
  ylab("Average Initial Rating") + 
  scale_y_continuous(limits = c(1, 7), breaks=seq(1, 7, 1)) +
  beckys.theme.conference +
  #geom_hline(aes(yintercept=0), size=.75) + 
  theme(axis.line.x=element_line(color = 'black'),legend.position = "none", axis.line.y=element_line(color = 'black'))

#ggsave("figures/meanRatingbyGroup.pdf", width=5, height=7, dpi=300)
```

## Statistical analysis of baseline differences
```{r baselineDiffsRegressions}


```

## Calculate absolute change across all conditions (our volitility measure)

```{r calculateAbsoluteChangeAverages, include=FALSE}
mageffect <- plyr::ddply(phase2merged, c("subjid", "group"), summarise, absratingchange=mean(absphasediffrating))
mageffect$group = factor(mageffect$group, levels = rev(levels(factor(mageffect$group))))
mag_summary = summarySE(mageffect, measurevar="absratingchange", groupvars=c("group"))

```

## Plot absolute change in preference rating graph 

```{r plotAbsoluteChange, echo=FALSE}
abs_point <-  ggplot(mageffect, aes(x=group, y=absratingchange, color=group, group=group)) 

abs_point + geom_point(position=position_jitterdodge(dodge.width=.7, jitter.width = .2), size=3, alpha=.5) + 
  scale_color_manual(values=c("#63ABD6","#1f78b4")) + 
  geom_errorbar(data=mag_summary, aes(ymin=absratingchange-se, ymax=absratingchange+se), width=.2, position=position_dodge(.7), size=1.2, alpha=1, color="black") +
  geom_point(data=mag_summary, position=position_dodge(.7), stat="identity", size=5, mapping=aes(x=group, y=absratingchange, color=group), alpha=1, color="black") + 
  xlab("Peer Feedback") + 
  ylab("Absolute Change in Preference") + 
  scale_y_continuous(limits = c(0, 1.7), breaks=seq(0, 1.8,.1), labels=abbreviate, expand = c(0,0)) +
  beckys.theme.conference +
  #geom_hline(aes(yintercept=0), size=.75) + 
  theme(axis.line.x=element_line(color = 'black'),legend.position = "none", axis.line.y=element_line(color = 'black'), axis.title.y=element_text(margin=margin(0, 10, 0, 0)))

#ggsave("figures/absoluteChangeDiss.pdf", width=5, height=7, dpi=300)
```

## Statistical analysis of volitility 

```{r volitilityRegressions}


```

# Social influence effects in young adolescents and adults
## Calculate residualized change (our social influence measure)

```{r calculateResidChange}

```

# Plot residualized change in preference rating

```{r plotResidChange, echo=FALSE}


```

## Statistical analysis of change in preference as function of social influence

```{r socInflRegressions}

```

