---
title: "BehavPaperCode"
author: "Rebecca Martin"
date: "7/11/2017"
output: 
    html_document:
        df_print: 'paged'
        toc: true
        toc_float:
            collapsed: false
            smooth_scroll: true
        number_sections: true
        code_download: true
        self_contained: true
        code_folding: 'hide'
---
# Set up 

## Settings

```{r settings}
knitr::opts_chunk$set(cache=TRUE)
```


```{r setDirs}
root <- rprojroot::find_rstudio_root_file()
dataDir <- file.path(root, 'data')
codeDir <- file.path(root, 'code')
figureDir <- file.path(root, 'figures')
```

## Packages

```{r libraries, message=FALSE, warning=FALSE}
library(reshape2)
library(plyr)
library(tidyverse)
library(lme4)
library(lmerTest)
library(effsize)
source(file.path(codeDir, "CreateFunctions.R"))
source(file.path(codeDir, "correlate_multiple_specific_variables.R"))
```

## Read in data

```{r readData}
raw <- read.table(file.path(dataDir, 'raw.txt'), header=TRUE, sep='\t')
phase2merged <- read.table(file.path(dataDir, 'new_anon.txt'), header=TRUE, sep='\t')
teens <- read.table(file.path(dataDir, 'teensonly.txt'), header=TRUE, sep='\t')
adults <- read.table(file.path(dataDir, 'adultsonly.txt'), header=TRUE, sep='\t')
averagedData <- read.table(file.path(dataDir, 'all_avgd_subset.txt'), header=TRUE, sep='\t')

phase2merged$group <- factor(phase2merged$group, labels = c("Adults", "Adolesc")) # changes levels for graphing
```


## Grand mean center and get adjusted means for plotting

```{r centerAndResidualize}
# all
p1_gmcenter = scale(phase2merged$phase1rating, scale=F)
phase2merged$p1rating_gmcenter <- p1_gmcenter
phase2merged$p1rating_gmcenter <- as.numeric(phase2merged$p1rating_gmcenter)

# teens
p1_gmcenter = scale(teens$phase1rating, scale=F)
teens$p1rating_gmcenter <- p1_gmcenter
teens$p1rating_gmcenter <- as.numeric(teens$p1rating_gmcenter)

# adults
p1_gmcenter = scale(adults$phase1rating, scale=F)
adults$p1rating_gmcenter <- p1_gmcenter
adults$p1rating_gmcenter <- as.numeric(adults$p1rating_gmcenter)

# residuals
adjmeans_all = lmer(phasediffrating ~ p1rating_gmcenter+(1+p1rating_gmcenter|subjid), data=phase2merged)
phase2merged$resid <- resid(adjmeans_all)

## Center by age group
phase2merged <- within(phase2merged, {phase1ratingGM = ave(phase1rating, group , FUN = mean)})
phase2merged$phase1ratingGC <- phase2merged$phase1rating - phase2merged$phase1ratingGM

## Make adjusted change scores (residuals controlling for time 1 ratings) for graphing
adjmeans_phasediffrating <- lmer(phasediffrating ~ phase1ratingGC + (1 + phase1ratingGC|subjid), data=phase2merged)
phase2merged$adjphasediffratingGV <- resid(adjmeans_phasediffrating)
```

## Make theme for plots

```{r makeTheme}
beckys.theme = theme(panel.background = element_rect(fill='transparent'),
                        axis.line = element_line(color='black'),
                        panel.grid.minor = element_line(color='transparent'),
                        axis.title.x = element_text(size=20, vjust=-.25),
                        axis.title.y = element_text(size=20, vjust=1),
                        axis.text.x = element_text(size=16, colour="black"),
                        axis.text.y = element_text(size=16, colour="black"),
                        legend.text=element_text(size=14))

beckys.theme.conference = theme(panel.background = element_rect(fill='transparent'),
                        axis.line = element_line(color='black'),
                        panel.grid.minor = element_line(color='transparent'),
                        axis.title.x = element_text(size=24, vjust=-.25, face = "bold"),
                        axis.title.y = element_text(size=24, vjust=1, face = "bold"),
                        axis.text.x = element_text(size=16, colour="black"),
                        axis.text.y = element_text(size=16, colour="black"),
                        legend.text=element_text(size=16),
                        strip.text.y = element_text(size = 16),
                        strip.text.x = element_text(size = 16))

beckys.theme.facet = theme(panel.background = element_rect(fill='transparent', colour="black"), # adds lines betw. panels
                        axis.line = element_line(color='black'),
                        panel.grid.minor = element_line(color='transparent'),
                        axis.title.x = element_text(size=20, vjust=-.25),
                        axis.title.y = element_text(size=20, vjust=1),
                        axis.text.x = element_text(size=16, colour="black"),
                        axis.text.y = element_text(size=14, colour="black"),
                        legend.text=element_text(size=14),
                        strip.text = element_text(size = 12),
                        strip.text.x = element_text(size = 16))
```

# Baseline differences between young adolescents and adults
## Distribution of ratings density plot

```{r distributionPlot}
distbytrial = ggplot(phase2merged, aes(x=phase1rating,fill=group)) + 
  geom_density(adjust=2, alpha=.7) + # add , colour=NA if want to take out black outlines
  beckys.theme +
  scale_x_continuous(limits = c(1, 7), breaks=seq(1, 7,1)) +
  scale_fill_manual(values=c("#1f78b4","#a6cee3")) + 
  scale_linetype_manual(values=c("#1f78b4","#a6cee3")) + 
  guides(fill = guide_legend(reverse = TRUE, override.aes = list(colour = NULL))) +
  xlab("Initial Ratings") +
  ylab("Density") +
  #theme(legend.key = element_rect(colour = "black"))
  beckys.theme.conference +
  theme(axis.line.x=element_line(color = 'black'),legend.position = "none", axis.line.y=element_line(color = 'black'))

distbytrial
```

## Calculate average ratings by group

```{r calculateAverageInitialRatings}
overallaverages <- plyr::ddply(phase2merged, c("subjid","group"), summarise, phase1rating=mean(phase1rating))
overallaverages$group = factor(overallaverages$group, levels = rev(levels(factor(overallaverages$group))))
overallavg_summary = summarySE(overallaverages, measurevar="phase1rating", groupvars=c("group"))

overallavg_summary
```

## Plot average initial ratings

```{r plotAverageInitialRating}
overallavg_point <-  ggplot(overallaverages, aes(x=group, y=phase1rating, color=group, group=group)) 
overallavg_point + geom_point(position=position_jitterdodge(dodge.width=.7, jitter.width = .2), size=3, alpha=.7) +
scale_color_manual(values=c("#6baed6","#1f78b4")) + 
  geom_errorbar(data=overallavg_summary, aes(ymin=phase1rating-se, ymax=phase1rating+se), width=.3, position=position_dodge(.7), size=1.5, alpha=1, color="black") +
  geom_point(data=overallavg_summary, position=position_dodge(.7), stat="identity", size=5, mapping=aes(x=group, y=phase1rating, color=group), alpha=1, color="black") + 
  xlab("Age Group") + 
  ylab("Average Initial Rating") + 
  scale_y_continuous(limits = c(1, 7), breaks=seq(1, 7, 1)) +
  beckys.theme.conference +
  #geom_hline(aes(yintercept=0), size=.75) + 
  theme(axis.line.x=element_line(color = 'black'),legend.position = "none", axis.line.y=element_line(color = 'black'))

#ggsave("figures/meanRatingbyGroup.pdf", width=5, height=7, dpi=300)
```

## Statistical analysis of baseline differences

```{r baselineDiffsRegressions}
# Does age group predict baseline ratings? 
baseline = lmer(p1rating_gmcenter ~ group + (1|subjid), data=phase2merged) 
summary(baseline)
confint(baseline, level=.9)
```

Get percentages for distribution differences
```{r distDescriptiveStats}
## Are means betw. groups different? 
groupmeans <- t.test(phase1rating ~ group, data=phase2merged, na.rm=TRUE)
groupmeans

groupmeans = ddply(phase2merged, .(subjid, group), summarise, initrating=mean(phase1rating))
groupsummary = summarySE(groupmeans, measurevar="initrating", groupvars="group")

## Do k-s test to show how distribution is different
ks.test(phase2merged$phase1rating[phase2merged$group=="YAs"], phase2merged$phase1rating[phase2merged$group=="Adults"], na.rm=TRUE)

## calculate proportions of neg, extreme and pos ratings
proportions <- phase2merged %>% group_by(group, subjid) %>% 
  summarise(Bottom=sum(phase1rating < 4)/n(),
            # | is or, & is and
            Extreme=sum(phase1rating <= 1 | phase1rating >= 7)/n(),
            Edges=sum(phase1rating <= 2 | phase1rating >= 6)/n(),
            Top=sum(phase1rating >= 5)/n())

var.test(Bottom ~ group, data=proportions)
var.test(Extreme ~ group, data=proportions)
var.test(Edges ~ group, data=proportions)
var.test(Top ~ group, data=proportions)

propBottom <- t.test(Bottom ~ group,var.equal=T, data=proportions, na.rm=TRUE) # easier way to do t-test
cohen.d(Bottom ~ group, data=proportions)

propExtreme <- t.test(Extreme ~ group, var.equal=T, data=proportions, na.rm=TRUE)
propEdges <- t.test(Edges ~ group, var.equal=T, data=proportions, na.rm=TRUE)
propTop <- t.test(Top ~ group, var.equal=T, data=proportions, na.rm=TRUE)
cohen.d(Top ~ group, data=proportions)

## regression of neg values
negval <- lm(Bottom ~ group, data=proportions)
summary(negval)
```

## Calculate absolute change across all conditions (our volitility measure)

```{r calculateAbsoluteChangeAverages}
mageffect <- plyr::ddply(phase2merged, c("subjid", "group"), summarise, absratingchange=mean(absphasediffrating))
mageffect$group = factor(mageffect$group, levels = rev(levels(factor(mageffect$group))))
mag_summary = summarySE(mageffect, measurevar="absratingchange", groupvars=c("group"))

mag_summary
```

## Plot absolute change in preference rating graph 

```{r plotAbsoluteChange}
abs_point <-  ggplot(mageffect, aes(x=group, y=absratingchange, color=group, group=group)) 

abs_point + geom_point(position=position_jitterdodge(dodge.width=.7, jitter.width = .2), size=3, alpha=.5) + 
  scale_color_manual(values=c("#63ABD6","#1f78b4")) + 
  geom_errorbar(data=mag_summary, aes(ymin=absratingchange-se, ymax=absratingchange+se), width=.2, position=position_dodge(.7), size=1.2, alpha=1, color="black") +
  geom_point(data=mag_summary, position=position_dodge(.7), stat="identity", size=5, mapping=aes(x=group, y=absratingchange, color=group), alpha=1, color="black") + 
  xlab("Group") + 
  ylab("Absolute Change in Preference") + 
  scale_y_continuous(limits = c(0, 1.7), breaks=seq(0, 1.8,.1), labels=abbreviate, expand = c(0,0)) +
  beckys.theme.conference +
  #geom_hline(aes(yintercept=0), size=.75) + 
  theme(axis.line.x=element_line(color = 'black'),legend.position = "none", axis.line.y=element_line(color = 'black'), axis.title.y=element_text(margin=margin(0, 10, 0, 0)))

ggsave(file.path(figureDir,"absoluteChangeDiss.pdf"), width=5, height=7, dpi=300)
```

```{r calculateAbsoluteChangeAveragesbyPeerCond}
mageffect <- plyr::ddply(phase2merged, c("subjid", "Phase1PCond2", "group"), summarise, absratingchange=mean(absphasediffrating))
mageffect$Phase1PCond2 = factor(mageffect$Phase1PCond2, labels = c("Less", "Agree", "More", "NoFb"))
mageffect$group = factor(mageffect$group, levels = rev(levels(factor(mageffect$group))))
mag_summary = summarySE(mageffect, measurevar="absratingchange", groupvars=c("Phase1PCond2", "group"))

mag_summary
```

```{r plotAbsoluteChangePlotbyPeerCond}
abs_point2 <-  ggplot(mageffect, aes(x=Phase1PCond2, y=absratingchange, color=group, group=group)) 

abs_point2 + geom_point(position=position_jitterdodge(dodge.width=.7, jitter.width = .2), size=3, alpha=.5) + 
  #scale_color_brewer(palette="Paired") +
  scale_color_manual(values=c("#6baed6","#1f78b4")) + 
  geom_errorbar(data=mag_summary, aes(ymin=absratingchange-se, ymax=absratingchange+se), width=.4, position=position_dodge(.7), size=1, alpha=1, color="black") +
  geom_point(data=mag_summary, position=position_dodge(.7), stat="identity", size=5, mapping=aes(x=Phase1PCond2, y=absratingchange, color=group), alpha=1, color="black") + 
  xlab("Peer Feedback") + 
  ylab("Absolute Change in Preference") + 
  scale_y_continuous(limits = c(0, 2.5), breaks=seq(0, 2.5,.25)) +
  xlim("NoFb", "Agree", "More", "Less") +
  #geom_hline(aes(yintercept=0), size=.75) + 
  theme(axis.line.x=element_line(color = 'black'),legend.position = "none", axis.line.y=element_line(color = 'black'), axis.title.y=element_text(margin=margin(0, 10, 0, 0))) +
    beckys.theme.conference

ggsave(file.path(figureDir,"absoluteChangeAllDiss.pdf"), width=8, height=7, dpi=300)
```

## Statistical analysis of volitility 

```{r volitilityRegressions}
### Change with random slopes

### Interaction
groupchangeinteraction = lmer(absphasediffrating ~ Phase1PeerDiff_combcontrol*group+(1+Phase1PeerDiff_combcontrol|subjid), data=phase2merged)
summary(groupchangeinteraction)
confint(groupchangeinteraction, level=0.9)

### Interaction no peer feedback
groupchangeinteraction2 = lmer(absphasediffrating ~ group+(1|subjid), data=phase2merged)
summary(groupchangeinteraction2)
```

# Social influence effects in young adolescents and adults
## Calculate residualized change (our social influence measure)

```{r calculateResidChange}
ageeffect = ddply(phase2merged, .(subjid, group, Phase1PCond2), summarise, diffscore=mean(resid))
ageeffect$Phase1PCond2 = factor(ageeffect$Phase1PCond2, labels = c("Less", "Agree", "More", "NoFb"))
ageeffect$group = factor(ageeffect$group, levels = rev(levels(factor(ageeffect$group))))
age_summary = summarySE(ageeffect, measurevar="diffscore", groupvars=c("Phase1PCond2", "group"))

age_summary
```

## Plot residualized change in preference rating

```{r plotResidChange}
age_point <-  ggplot(ageeffect, aes(x=Phase1PCond2, y=diffscore, color=group, group=group)) 

age_point + geom_point(position=position_jitterdodge(dodge.width=.7, jitter.width = .2), size=2, alpha=.5) +
    scale_color_manual(values=c("#6baed6","#1f78b4")) + 
  geom_errorbar(data=age_summary, aes(ymin=diffscore-se, ymax=diffscore+se), width=.4, position=position_dodge(.7), size=1, alpha=1, color="black") +
  geom_point(data=age_summary, position=position_dodge(.7), stat="identity", size=4, mapping=aes(x=Phase1PCond2, y=diffscore), alpha=1, color="black") + 
  xlab("Peer Feedback") + 
  ylab("Change in Preference") + 
  scale_y_continuous(limits = c(-1, 1), breaks=seq(-1, 1,.1), labels=function(x) round(x, 2)) +
  xlim("NoFb", "Agree", "More", "Less") +
  beckys.theme.conference +
  geom_hline(aes(yintercept=0), size=.75) + 
  theme(axis.line.x=element_line(color = 'black'),legend.position = "none", axis.line.y=element_line(color = 'black'))

ggsave(file.path(figureDir,"BehavMainEffectsDiss.pdf"), width=7, height=5, dpi=300)
```

## Statistical analysis of change in preference as function of social influence

```{r socInflRegressions}
### Conformity with random slopes
#### Note: pos_neg is a -1, 0, 1 variable where -1=peers lower, 0=peers agree or no feedback, 1=peers higher

## Main effect of Peer Cond for teens
teenresults <- lmer(phasediffrating ~ p1rating_gmcenter + pos_neg + (1 + p1rating_gmcenter + pos_neg|subjid), data=teens)
summary(teenresults)
confint(teenresults, level=0.9)

## Main effect of Peer Cond for adults
adultresults = lmer(phasediffrating ~ p1rating_gmcenter+pos_neg+(1+p1rating_gmcenter+pos_neg|subjid), data=adults)
summary(adultresults)
confint(adultresults, level=0.9)

## Interaction with teens and adults?
groupinteraction = lmer(phasediffrating ~ p1rating_gmcenter+pos_neg*group+(1+p1rating_gmcenter+pos_neg|subjid), data=phase2merged)
summary(groupinteraction)
confint(groupinteraction, level=0.9)
```

# Individual Differences Analysis

## Prepare conformity data

```{r indDiffSubsets}
droplevels <- c("-1","1")
disagree <- phase2merged[phase2merged$Phase1PCond2 %in% droplevels,]
disagree <- droplevels(disagree)

testconform <- plyr::ddply(disagree, .(subjid, group), summarise, phase1Av=mean(phase1rating), conformAv=mean(conform))   
averagedData$phase1 <- testconform$phase1Av
averagedData$conform2 <- testconform$conformAv

# conform fixed effects model
conformMod <- lm(conform2 ~ phase1, data=averagedData)
averagedData$conformresid <- resid(conformMod)

# Rename everything for plotting
averaged3 <- plyr::rename(averagedData, c("conformresid"="ConformityScore","STAI_CombZ"="AnxietyZ","BDI_Z"="DepressionZ", "RPI"="ResistancetoPeerInfluence","n2belong"="NeedToBelong","SCOFF"="DisorderedEating", "BMI.Group"="BMIGroup", "WASI.IQ"="IQ", "TAS"="Alexithymia","MMIS"="MediaInfluence", "BESC"="BodyImage", "CDI_BDI"="Depression", "STAI_Combined"="Anxiety", "TAN.MEAN"="PubertalStatus", "CRSQ.Anxiety.RSQ"="RejectionSensitivity", "MCSD"="SocialDesirability","SDS"="SocialDesirabilityTeens","YRBSS_Dieting"="DietingStatus","YRBSS_Health_index"="HealthyEating","YRBSS_Self_described_weight"="SelfDescribedWeight", "RSQ_Z"="RejectionSensitivity_Z", "SocDesire_Z"="SocialDesirabilityZ"))

# change levels
averaged3$group = factor(averaged3$group, levels = rev(levels(factor(averaged3$group))))

# Rename for lmer regression
phase2merged2 <- plyr::rename(phase2merged, c("phasediffrating"="RatingChange","p1rating_gmcenter"="InitialRating", "Sex"="Gender", "group"="AgeGroup", "pos_neg"="SocialInfluence","STAI_CombZ"="AnxietyZ","BDI_Z"="DepressionZ", "RPI"="ResistancetoPeerInfluence","n2belong"="NeedToBelong","SCOFF"="DisorderedEating", "BMI.Group"="BMIGroup", "WASI.IQ"="IQ", "TAS"="Alexithymia","MMIS"="MediaInfluence", "BESC"="BodyImage", "CDI_BDI"="Depression", "STAI_Combined"="Anxiety", "TAN.MEAN"="PubertalStatus", "CRSQ.Anxiety.RSQ"="RejectionSensitivity", "MCSD"="SocialDesirability","SDS"="SocialDesirabilityTeens","YRBSS_Dieting"="DietingStatus","YRBSS_Health_index"="HealthyEating","YRBSS_Self_described_weight"="SelfDescribedWeight", "RSQ_Z"="RejectionSensitivityZ", "SocDesire_Z"="SocialDesirabilityZ"))

# Prepare for correlations
averaged3$sex2 <- as.factor(averaged3$Sex)
averaged3$sex2 <- as.numeric(averaged3$sex2)

teenStuff <- averaged3[which(averaged3$group == "teens"),]
teenStuff <- droplevels(teenStuff)
teensAll <- subset(teenStuff, select=c("ConformityScore", "conform2", "Sex", "Age", "IQ","Edu", "Degree", "Depression", "Anxiety", "PubertalStatus", "ResistancetoPeerInfluence", "NeedToBelong", "MediaInfluence", "RejectionSensitivity", "SocialDesirabilityTeens", "HungerLevel", "Atetime", "DisorderedEating", "BodyImage", "BMI_Percentile", "SelfDescribedWeight", "DietingStatus", "HealthyEating"))

adultStuff <- averaged3[which(averaged3$group == "adults"),]
adultStuff <- droplevels(adultStuff)
adultsAll <- subset(adultStuff, select=c("ConformityScore", "conform2", 'Sex', "Age", "Depression", "Anxiety", "ResistancetoPeerInfluence", "NeedToBelong", "MediaInfluence", "RejectionSensitivity", "SocialDesirability", "HungerLevel", "Atetime", "DisorderedEating", "BMI", "SelfDescribedWeight", "DietingStatus", "HealthyEating"))

allgroups <- subset(averaged3, select=c("ConformityScore", "conform2", "Sex", "Age", "DepressionZ", "AnxietyZ", "ResistancetoPeerInfluence", "NeedToBelong", "MediaInfluence", "RejectionSensitivity_Z", "SocialDesirabilityZ", "HungerLevel", "Atetime", "DisorderedEating", "BMIGroup", "SelfDescribedWeight", "DietingStatus", "HealthyEating"))
```

## Get Individual Differences Correlations

```{r IndDiffsCorr}
multicor.sig(adultsAll[,1:2], adultsAll[,4:18], "corrResults/adultIndDiffscorrsig.txt")
multicor.sig(teensAll[,1:2], teensAll[,4:23], "corrResults/teenIndDiffscorrsig.txt")

multicor(adultsAll[,1:2], adultsAll[,4:18], "corrResults/adultIndDiffscorr.txt")
multicor(teensAll[,1:2], teensAll[,4:23], "corrResults/teenIndDiffscorr.txt")

## All groups
multicor.sig(allgroups[,1:2], allgroups[,4:18], "corrResults/allIndDiffscorrsig.txt")
multicor(allgroups[,1:2], allgroups[,4:18], "corrResults/allIndDiffscorr.txt")

## gender? 
multicor.sig(averaged3[,61:62], averaged3[,6:39], "corrResults/genderIndDiffscorr.txt")
```

## Statistical Analysis of Individual differences data

```{r indDiffRegression}
everything <- lmer(RatingChange ~ InitialRating+SocialInfluence+AgeGroup+Gender+DepressionZ+AnxietyZ+ResistancetoPeerInfluence+NeedToBelong+RejectionSensitivityZ+SocialDesirabilityZ+HungerLevel+Atetime+BMIGroup+DisorderedEating+MediaInfluence+SelfDescribedWeight+DietingStatus+HealthyEating+(1+InitialRating+SocialInfluence|subjid), data=phase2merged2)

summary(everything)
```


## Make individual difference plots

### General Health Measures

```{r genHealthPlots}

# General Health
general <- subset(averaged3, select=c("subjid", "ConformityScore","group", "Age", "AnxietyZ", "DepressionZ")) 
general2 <- melt(averaged3, id.vars=c("subjid", "group", "ConformityScore"), measure.vars=c("Age", "AnxietyZ","DepressionZ")) 

# General scatter plot 
generalscatter <- ggplot(general2, aes(x=value, y=ConformityScore, colour=group)) 
generalscatter + 
  geom_point() + 
  scale_color_brewer(palette="Paired") +
  geom_smooth(method="lm", se=TRUE) +
  facet_wrap( ~ variable, scales="free") +
  ylab("Residualized Conformity Score") + 
  beckys.theme.facet +
  #scale_y_continuous(limits = c(-.2,.2), breaks=seq(-.4,.4,.05), labels=abbreviate, expand = c(0,0)) + 
  geom_hline(aes(yintercept=0), size=.25) 
  
# ggsave - make super wide
```

### Gender

```{r genderPlot}
## Gender
gender_summary = summarySE(averaged3, measurevar="ConformityScore", groupvars=c("Sex", "group"))

genderscatter <- ggplot(averaged3, aes(x=Sex, y=ConformityScore, colour=group, fill=group)) 
genderscatter + 
  geom_point(position=position_jitterdodge(jitter.width=.4, dodge.width=.4), alpha=.7)  +
  geom_point(data=gender_summary, position=position_dodge(.4), stat="identity", size=3, mapping=aes(x=Sex, y=ConformityScore), colour="black") +
  geom_errorbar(data=gender_summary, aes(ymin=ConformityScore-se, ymax=ConformityScore+se), width=.2,position=position_dodge(.4), size=0.7, colour="black") +
  scale_color_brewer(palette="Paired") +
  ylab("Conformity Score") + 
  beckys.theme.conference +
  geom_hline(aes(yintercept=0), size=.25) 

# ggsave 
```

### Social Individual Differences

```{r socialPlots}
social <- subset(averaged3, select=c("subjid","ConformityScore", "ResistancetoPeerInfluence", "NeedToBelong","SocialDesirabilityZ", "RejectionSensitivity_Z", "MediaInfluence"))  
social2 <- melt(averaged3, id.vars=c("subjid", "group", "ConformityScore"), measure.vars=c("ResistancetoPeerInfluence", "NeedToBelong","SocialDesirabilityZ", "RejectionSensitivity_Z", "MediaInfluence"))

socialscatter <- ggplot(social2, aes(x=value, y=ConformityScore, colour=group)) 
socialscatter + 
  geom_point() + 
  scale_color_brewer(palette="Paired") +
  geom_smooth(method="lm", se=TRUE) +
  facet_wrap( ~ variable, scales="free") +
  ylab("Conformity Score") + 
  beckys.theme.facet +
  geom_hline(aes(yintercept=0), size=.25)

# ggsave - make super wide
```

### Food and Eating Health Habit Plots

```{r foodPlots}
food <- subset(averaged3, select=c("subjid", "group", "ConformityScore","HungerLevel", "Atetime", "DisorderedEating", "BMIGroup","BodyImage", "SelfDescribedWeight", "DietingStatus", "HealthyEating"))
food2 <- melt(averaged3, id.vars=c("subjid", "group", "ConformityScore"), measure.vars=c("HungerLevel", "Atetime", "DisorderedEating", "BMIGroup","BodyImage", "SelfDescribedWeight", "DietingStatus", "HealthyEating"))

foodscatter <- ggplot(food2, aes(x=value, y=ConformityScore, colour=group)) 
foodscatter + 
  geom_point() + 
  scale_color_brewer(palette="Paired") +
  geom_smooth(method="lm", se=TRUE) +
  facet_wrap( ~ variable, scales="free") +
  ylab("Conformity Score") + 
  beckys.theme.facet +
  geom_hline(aes(yintercept=0), size=.25) 

# ggsave - make extra wide
```

